Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed a comment in the discussion section

\subsection{Follower effect on build success}

\todo{Maybe ``relationship with'' rather than ``effect on''?}

@@

Overall, we have found that social attributes which proxy experience\todo{, such
  as, example,} produce a 
noticeable increase in predicting build success.  While the increase was noticeable 
with the full data set, there was a much greater increase in prediction
accuracy after performing downsampling. These results show that social factors
as the ones studied in this paper are significant predictors when
evaluating the predictive power of build commit success.

>>>>

\subsection{Follower relationship with build success}

@@

Overall, we have found that social attributes which proxy experience, such if
the developer is a core contributor for the project, produce a 
noticeable increase in predicting build success.  While the increase was noticeable 
with the full data set, there was a much greater increase in prediction
accuracy after performing downsampling. These results show that social factors
as the ones studied in this paper are significant predictors when
evaluating the predictive power of build commit success.
